---
title: "Prediction Assignment Writeup"
author: "g. gambino"
date: "1/1/2020"
output: html_document
---

## Overview

The goal of your project is to predict the manner in which they did the exercise. This is the "classe" variable in the training set. You may use any of the other variables to predict with. You should create a report describing how you built your model, how you used cross validation, what you think the expected out of sample error is, and why you made the choices you did. You will also use your prediction model to predict 20 different test cases.

 
### Library
```{r}
library(e1071)
library(caret)
library(knitr)
library(randomForest)
library(rpart)
library(rpart.plot)
library(rattle)
```

### Acquisition Dataset process
```{r load data}
trainLink <- "https://d396qusza40orc.cloudfront.net/predmachlearn/pml-training.csv"
testLink <- "https://d396qusza40orc.cloudfront.net/predmachlearn/pml-testing.csv"
trainData <- read.csv(url(trainLink), na.strings = c("NA", "#DIV/0!", ""))
testData <- read.csv(url(testLink), na.strings = c("NA", "#DIV/0!", ""))
trainData <- trainData[, colSums(is.na(trainData)) == 0]
testData <- testData[, colSums(is.na(testData)) == 0]
```
### Data cleaining
```{r data clean}
trainData <- trainData[, -c(1:7)]
testData <- testData[, -c(1:7)]
```

### Making training and test set 
```{r data train and test}
trainPartitionData <- createDataPartition(trainData$classe,  p = 0.7, list = F)
trainDataSet <- trainData[trainPartitionData, ]
testDataSet <- trainData[-trainPartitionData, ]
dim(trainData); dim(testDataSet)
```

### Decision tree model

```{r feature decision tree}
decisionTreeModel <- rpart(classe ~ ., data = trainDataSet, method = "class")
decisiontreeprediction <- predict(decisionTreeModel, testDataSet, type = "class")
```


### Plot Decision Tree Model with Fancy
```{r fancy plot}
fancyRpartPlot(decisionTreeModel, main = "Fancy plot")
```

### Plot Decision Tree with Rpart
```{r rpart plot}
rpart.plot(decisionTreeModel, main = "Rpart plot", under = T, faclen = 0)
```

### Using confusion matrix to test results
```{r confusion matrix}
confusionMatrix(decisiontreeprediction, testDataSet$classe)
```


## Random forest model
```{r random forest}
randomforestmodel <- randomForest(classe ~. , data = trainDataSet, method = "class")
randomForestPrediction <- predict(randomforestmodel, testDataSet, type = "class")
confusionMatrix(randomForestPrediction, testDataSet$classe)
```


## Final results
Random Forest accuracy is better.
with Decision tree we have accuracy value 0.75 approx. Random forest model has a value of 0.99 approx.

```{r final prediction}
finalpredict <- predict(randomforestmodel, testDataSet, type = "class")
head(finalpredict)
```
